Information Disclosure in Dynamic Innovation Contests

### 2025-05-10 paper/Paper.tex
update-paper

First of all, we assume that time is discretized into uniform intervals of length $\Delta$.
By definition, the likelihood function of a realization of the representative player $i$'s submission events $\{t^i_k\}_{k=1}^{N_i}$ is given by 
\begin{equation}\label{eq-ihpp-prob}
p\left(\{\hat{t}^i_k\}_{k=1}^{N_i} | \tau_i\right) = \exp\left\{-\int_{s\in\mathcal{T}}\tau_i(s)ds\right\}\prod_{k=1}^{N_i}\tau_i(\hat{t}^i_k)
\end{equation}
where $\tau_i$ is defined in (\ref{eq-model-intensity}). 
Here, the integrals in the left hand size can be approximated by summations.
Similar to the other player $j$. 
Next, suppose we sample the leaderboard gap $\hat{y}_t$ at time points $(t_1, t_2, ..., t_N)$, obtaining observations $\{\hat{y}_{t_k}\}^N_{k=1}$. 
Let $t_0 = 0$ and suppose the initial gap $y_0$ follows $\mathcal{N}(\mu_0, \sigma_0)$. 
Then, according to the assumed data-generating process of $\hat{y}_t$ in (\ref{eq-leaderboard-gap}), the corresponding likelihood function is
\begin{equation}\label{eq-obs_gap-prob}
\begin{aligned}
p&\left(\{\hat{y}_{t_k}\}_{k=1}^N | m_i, m_j\right) = 
\phi\left(y_0 | \mu_0, \sigma_0\right) \times\\
&\quad\prod_{k=0}^{N-1}\phi\left(\hat{y}_{t_{k+1}}-\hat{y}_{t_k}|\int_{t_k}^{t_{k+1}}m_i(\tilde{y}_s, s) - m_j(\tilde{y}_s, s)ds, \sigma^2(t_{k+1}-t_k)+\frac{1}{\Delta\lambda}\right)
\end{aligned}
\end{equation}
where $\hat{y}_{t_0} = y_0$.

To evaluate the likelihood functions (\ref{eq-ihpp-prob}) and (\ref{eq-obs_gap-prob}), we must first compute the equilibrium trajectories of both the perceived output gap $(\tilde{y}_t)$ and the effort levels $(m_i(\tilde{y}_t, t), m_j(\tilde{y}_t, t))$, as implied by equations (\ref{eq-equilibrium-effort}) and (\ref{eq-fintered-y-update}). 
Importantly, the construction of $\tilde{y}$ and the effort functions $m_i$ and $m_j$ depends on the underlying (unobserved) parameters $c_i$, $c_j$, $\sigma$, $\lambda$, $r$, $\mu_0$ and $\sigma_0$, which are themselves subject to estimation.
We denote these underlying parameters collectively as $\mathcal{P}$.

@@

Unknown parameters to be estimated: 
\begin{itemize}
	\item $\sigma$ (Total innovation risk): prior - truncated normal
	\item $c_i$ and $c_j$ (Capacities): prior - truncated normal
\end{itemize}

@@

\subsection{Bayesian Inference}

>>>>

First of all, we assume that time is discretized into uniform intervals of length $\Delta$.
By definition, the likelihood function of a realization of the representative player $i$'s submission events $\{t^i_k\}_{k=1}^{N_i}$ is given by 
\begin{equation}\label{eq-ihpp-prob}
p\left(\{\hat{t}^i_k\}_{k=1}^{N_i} | \tau_i\right) = \exp\left\{-\int_{s\in\mathcal{T}}\tau_i(s)ds\right\}\prod_{k=1}^{N_i}\tau_i(\hat{t}^i_k)
\end{equation}
where $\tau_i$ is defined in (\ref{eq-model-intensity}). 
Here, the integrals in the left hand size can be approximated by summations.
Similar to the other player $j$. 
Next, suppose we sample the leaderboard gap $\hat{y}_t$ at time points $(t_1, t_2, ..., t_N)$, obtaining observations $\{\hat{y}_{t_k}\}^N_{k=1}$. 
Let $t_0 = 0$ and suppose the initial gap $y_0$ is zero. 
Then, according to the assumed data-generating process of $\hat{y}_t$ in (\ref{eq-leaderboard-gap}), the corresponding likelihood function is
\begin{equation}\label{eq-obs_gap-prob}
p\left(\{\hat{y}_{t_k}\}_{k=1}^N | m_i, m_j\right) = 
\prod_{k=1}^{N}
\phi\left(\{\hat{y}_{t_k}\}_{k=1}^N | \left\{\mu_k\right\}^N_{k=1}, \Sigma_y+\frac{1}{\Delta\lambda}I_N\right)
\end{equation}
where $\mu_k = \int_{0}^{t_{k}}m_i(\tilde{y}_s, s) - m_j(\tilde{y}_s, s)ds$ and $\Sigma_y(i, j) = \sigma^2\min(t_i,t_j)$.

To evaluate the likelihood functions (\ref{eq-ihpp-prob}) and (\ref{eq-obs_gap-prob}), we must first compute the equilibrium trajectories of both the perceived output gap $(\tilde{y}_t)$ and the effort levels $(m_i(\tilde{y}_t, t), m_j(\tilde{y}_t, t))$, as implied by equations (\ref{eq-equilibrium-effort}) and (\ref{eq-fintered-y-update}). 
Importantly, the construction of $\tilde{y}$ and the effort functions $m_i$ and $m_j$ depends on the underlying (unobserved) parameters $c_i$, $c_j$, $\sigma$ and $\lambda$, which are themselves subject to estimation.
We denote these underlying parameters collectively as $\mathcal{P}$.

@@

In our Bayesian framework, we specify truncated normal distributions with large variances as priors for the unknown parameters $c_i$, $c_j$, $\sigma$ and $\lambda$.  
This choice is intended to make the priors as uninformative as possible, thereby minimizing their influence on the posterior distribution. 
By allowing the parameters to vary broadly within reasonable bounds, these weakly informative priors let the data play a dominant role in shaping the inference, while still ensuring mathematical well-posedness and numerical stability.

@@

\subsection{Asymptotic Convergence}
